---
title: "NEWS"
output: 
  github_document:
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
library(ggedit)
knitr::opts_chunk$set(echo = TRUE)
r <- getOption("repos")
  r["CRAN"] <- "http://cran.cnr.berkeley.edu/"
  options(repos = r)
```

# 0.4.0
## Update
Bump R version to align with native pipe

# 0.4.0
## Update
Refactor functions to align with `ggplot2` version (3.5.0). 

  - Replace plyr with purrr dependency
  - Update faceting cloning to support new formals in `ggplot2`

# 0.2.6
## Update
Collapse internal files to run the module and gadget from same base script.

Reorganize BS Modals to have columns by object type.

Change plot.ggedit be a print.ggedit method.

`shinyBS` js library dependencies loaded with package, this lets ggedit run on attachment. i.e. `ggedit::ggedit(p)`
    
## Add

**margins** can be edited in the theme UI

`+.gg` functionality added to *gglist* class to manipulate to multiple plots in layout
    
```{r,eval=FALSE}

as.gglist(list(pList[[1]],pList[[3]])) + 
  geom_hline(yintercept=3:4,linetype=2) + 
  theme_minimal()+
  theme(legend.position = 'top')

```
  
**gg_session** retreives all functions that create ggroto layers or stats in current loaded namespace and returns unique mapping to their `position`,`geom`,`stat`.
  
```{r,eval=FALSE}

gg_session()

```
  
**gg_vetting** returns the columns from gg_session relevant to a compiled plot
  
```{r,eval=FALSE}

gg_vetting(pList$pointSmooth)

```

**ggedit_opts** functionality to control session levels options (like `knitr::opts_chunk`). This can be used to manipulate the package defaults like the theme tips seen in BS modals. It is also used to store an updated output of gg_session, so ggedit can identify the correct mapping with gg_extension pacakges (eg `ggalt`).
  
```{r,eval=FALSE}

library(ggalt)

ggedit_opts$set(list(session_geoms=gg_session()))

ggedit_opts$get('session_geoms')

```
  
manipulate gg_extension pacakges (still in development, but works for a lot of the [ggplot2 extension packages](https://ggplot2-exts.org/))
  
**dput.ggedit** returns dput for ggplot2 object in script form and not a structure.
  
```{r,eval=FALSE}
pList$pointSmooth #original compiled plot
this.gg <- dput.ggedit(pList$pointSmooth) #dput the plot
writeLines(this.gg) #show the output
eval(parse(text=this.gg)) #recompile the plot
```
  
**summary.ggedit** method for ggedit class return script that created compiled gg object. 

```{r,eval=FALSE}
out <- ggedit(pList[1:2])
#assuming out is returned from ggedit
summary(out)

# point
# ggplot(mapping=aes(x=Sepal.Length,y=Sepal.Width),[data.frame])+
# geom_point(aes(colour=Species),size=6)
# 
# pointWrap
# ggplot(mapping=aes(x=Sepal.Length,y=Sepal.Width),[data.frame])+
# geom_point(aes(colour=Species),size=6)+
# facet_wrap(facets=~Species,shrink=TRUE)
```

# 0.2.2
## Update 
  - Change `mutate_each` with `mutate_all` to be compatible with new `dplyr` release

## Add
    - can pass functions into stat_summary, eg `stat_summary(fun.y=mean_sd, geom='point')`
    - data.frames in layers are embedded as structures in verbose outputs, e.g. `geom_point(data=mtcars, aes(cyl, mpg))` will return
    ```r
    [1] "geom_point(mapping=aes(x=cyl,y=mpg), data=structure(list(mpg = c(21, 21, 22.8, 21.4, 18.7, 18.1, 14.3,
    24.4, 22.8, 19.2, 17.8, 16.4, 17.3, 15.2, 10.4, 10.4, 14.7, 32.4,.. <truncated>
    ```
    - aesthetic can be set to NULL, ie aes(group=NULL)