# Deploying

  - from the console: `ggedit(p)`
    
  - from the addin toolbar: highlight script of a plot object on the source editor window of RStudio and run from toolbar.
    
  - Shiny: use the Shiny module syntax to call the ggEdit UI elements.
    - server: `callModule(ggEdit,'pUI',obj=reactive(p))`
    - ui: `ggEditUI('pUI')`
    
## Console
To run ggedit all you need is a compiled ggplot plot object

```{r,echo=TRUE,eval=FALSE}
ggedit(p,...)
```

the following arguments can be passed in to the  ellipses
    
  - **verbose** logical to control if the output includes script for layers and themes calls for parsing to create objects (default, `verbose=TRUE`)

  - **showDefaults** toggle to control if the verbose output shows all the input arguments passed to the proto object (if `verbose==FALSE` then ignored)

  - **width,height** dimensions of the renderPlot where the active plot is displayed

  - **viewer** shiny viewer options. It can be either paneViewer (default with `minHeight=1000`), dialogViewer, browserViewer

## Addin

To launch the Shiny gadget from the addin menu highlight the code that creates the plot object or the plot name in the source pane of Rstudio, then click on the ggedit addin from the Addins the dropdown menu.

<iframe width="100%" height="400" src="https://www.youtube.com/embed/693XhHt8fug" frameborder="0" allowfullscreen></iframe>

## Shiny

Using ggedit as a Shiny module creates a self contained user interface layout that contains a ggedit interface for rendered plots created in a Shiny application. This means that you can launch as many ggedit environments as you need, replacing the static renderPlot with an interactive editable ggplot. 

To call the Shiny module you need a UI and server call:

  - server: `callModule(ggEdit,'pUI',obj=reactive(p))`
  - ui: `ggEditUI('pUI')`
  
Video of Shiny app example

<iframe width="100%" height="400" src="https://www.youtube.com/embed/pJ1kbd_OVwg" frameborder="0" allowfullscreen></iframe>

Script to reproduce the video app:

```{r echo=T,eval=FALSE}
library(ggedit)
library(shinyAce)
ui <-fluidPage(
  conditionalPanel("input.tbPanel=='b'",
               sidebarPanel(uiOutput('x1'),uiOutput('x2'))
               ),
  mainPanel(
    tabsetPanel(id = 'tbPanel',
    tabPanel('renderPlot/plotOutput',value = 'a',plotOutput('p')),
    tabPanel('ggEdit/ggEditUI',value = 'b',ggEditUI("pOut1")),
    tabPanel('ggEdit/ggEditUI with lists of plots',value = 'c',ggEditUI("pOut2"))
  )
  )
  
)

server <- function(input, output,session) {
  p1=iris%>%ggplot(aes(x=Sepal.Length,y=Sepal.Width,colour=Species))+geom_point()
  p2=iris%>%ggplot(aes(x=Sepal.Length,y=Sepal.Width,colour=Species))+geom_line()+geom_point()
  p3=list(p1=p1,p2=p2)

  output$p<-renderPlot({p1})
  outp1<-callModule(ggEdit,'pOut1',obj=reactive(list(p1=p1)))
  outp2<-callModule(ggEdit,'pOut2',obj=reactive(p3),showDefaults=T,height=300)

  output$x1<-renderUI({
    layerTxt=outp1()$UpdatedLayerCalls$p1[[1]]
            aceEditor(outputId = 'layerAce',value=layerTxt,
                      mode = "r", theme = "chrome", 
                      height = "100px", fontSize = 12,wordWrap = T)
         })  
  
  output$x2<-renderUI({
    themeTxt=outp1()$UpdatedThemeCalls$p1
    aceEditor(outputId = 'themeAce',value=themeTxt,
              mode = "r", theme = "chrome", 
              height = "100px", fontSize = 12,wordWrap = T)
  })  

}

shinyApp(ui, server)
```