#Package Functions

## ggedit
```{r results='asis',echo=FALSE}
fn.src('ggedit','ggedit',hlp.dir)
```

## ggEdit
```{r results='asis',echo=FALSE}
fn.src('ggEdit_Module','ggedit',hlp.dir)
```

## rgg

```{r results='asis',echo=FALSE}
fn.src('rgg','ggedit',hlp.dir)
```

After you finish editing the plots the natural progression is to use them in the rest of the script. In ggedit there is the function rgg (remove and replace ggplot). Using this function you can chain into the original code changes to the plot without multiplying script needlessly.

<iframe width="100%" height="600" src="https://www.youtube.com/embed/0QmJHwoWQWM" frameborder="0" allowfullscreen></iframe>


  - Specify which layer you want to remove from a plot:

`ggObj%>%rgg('line')`

  - Provide an index to a specific layer, in instances where there are more than one layer of the same type in the plot

`ggObj%>%rgg('line',2)`

  - Remove a layer from ggObj and replace it with a new one from the ggedit output p.out

`ggObj%>%rgg('line',newLayer = p.out$UpdatedLayers)`

  - Remove a layer and replace it with a new one and the new theme 

`ggObj%>%rgg('line',newLayer = p.out$UpdatedLayers)+p.out$UpdatedThemes`

## remove_geom
```{r results='asis',echo=FALSE}
fn.src('remove_geom','ggedit',hlp.dir)
```

## gggsave
generalized ggsave to save multiple outputs of ggplot to single file and multiple files from a single call. Plots can be saved to various graphic devices. 

```{r results='asis',echo=FALSE}
fn.src('gggsave','ggedit',hlp.dir)
```

```{r,results='markup',eval=FALSE,echo=TRUE}
#single file output to pdf
gggsave('Rplots.pdf',plot=pList)

#multiple file output to pdf
gggsave('Rplots.pdf',plot=pList,onefile=F)

#multiple file output to png
gggsave('Rplots.png',plot=pList)
```

## compare
```{r results='asis',echo=FALSE}
fn.src('compare','ggedit',hlp.dir)
```

## cloneLayer
```{r results='asis',echo=FALSE}
fn.src('cloneLayer','ggedit',hlp.dir)
```

## print.ggedit
```{r results='asis',echo=FALSE}
fn.src('print.ggedit','ggedit',hlp.dir)
```
